{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
naming

	\subsection{Lemma} \label{Proof1}
	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the Eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}. The coefficients $\xi^{m}$ corresponding to Eigenfunctions $\nu^m$ satisfy the following properties:

>>>>

	\subsection{Lemma (Three Traits of Scores)} \label{Proof1}
	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the Eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}. The coefficients $\xi^{m}$ corresponding to Eigenfunctions $\nu^m$ satisfy the following properties:
